Cognitive and ecological aspects determine cleaner performance

### 2021-11-26 manuscript_1.0.Rmd
Included some of Red1 comments. Updated figure 1.

One example of strategic adjustment in a biological market is the marine cleaning 
mutualism involving the cleaner
fish *Labroides dimidiatus* and 'client' fish. Clients offer themselves as
food patches for cleaners to remove ectoparasites, which gives the
cleaners calories and the clients improved health
[@waldie_LongTerm_2011; @ros_Does_2011,@triki_Effects_2016]. As
cleaners have about 2000 interactions per day
[@grutter_Relationship_1995], they regularly face the situation that
two clients seek cleaning simultaneously. In such conditions, it is
important to distinguish between 'resident' and 'visitor' client species
[@bshary_Cleaner_2001a]. The residents have small home ranges and hence
access to only the local cleaner, while the visitors have large home
ranges and hence access to two or more cleaners. Thus, visitors have the
option to switch to another cleaner if being made to wait, while
residents must wait for inspection. Indeed, visitors have been observed
to use their partner choice options in that way [@bshary_Choosy_2002],
which may explain why cleaners give visitors service priority in a field
study in the Red Sea [@bshary_Cleaner_2001a]. Furthermore, early
laboratory experiments showed that leaving causes service priority
[@bshary_Asymmetric_2002]. The experiments consisted of a simultaneous
two-choice task, where cleaners had to decide which of two Plexiglas
plates to approach first and eat mashed prawn of it. One plate was made
to behave like a resident, i.e. it would remain until the cleaner had
eaten off it. The other plate was made to behave like a visitor, i.e. it
would be removed if not inspected first. Cleaners learned to prefer the
visitor plate and hence obtained the double amount of food
[@bshary_Asymmetric_2002]. Adult cleaner fish outperform various
primates as well as rats and pigeons in this original version of the
biological market task [@salwiczek_Adult_2012; @zentall_Early_2017];
only African grey parrots solve this task as well [@pepperberg_Can_2014].

Recent research has refined our view on partner choice and priority of
access in the *L. dimidiatus* cleaning mutualism, and as a consequence
performance in the biological market task. First, details of the task
presentation may matter; i.e. what relevant information is encoded in
the design of the two plates (colour versus size; @wismer_Cuebased_2019), or
whether the information is in the colour of the food
[@pretot_Comparative_2021; @pretot_Comparing_2016], and whether the
food is visible or hidden/released only when the subjects made choices
on a touch screen [@pretot_Factors_2016]. Second, it appears that cleaner and
client densities in nature affect how cleaners perform in the original
market task: when densities are low, cleaners are more likely to fail to
complete the task [@triki_Biological_2019; @triki_Decrease_2018;
@wismer_Variation_2014]. The apparent explanation for this failure is that visitor
clients are less likely to exert their choice options (and hence wait
for inspection if made to wait) when cleaner fish densities are low
[@triki_Brain_2020]. This change in behaviour may be due to the fact that
when cleaner densities are low, the cost of switching in terms of
distance to swim and time invested increases. If visitors are not
choosy, cleaners should not give them priority anymore. Interestingly,
while cleaners from high-density areas have larger forebrains harbouring
more cells than cleaners from low-density areas [@triki_Brain_2020], on a
local scale those individuals that perform in the market task in a way
that corresponds to the locally optimal strategy (solving/failing the
task when living in high/low density) have relatively larger forebrains
[@triki_Brain_2020]. Taken together, recent empirical results clearly show
that cognitive processes are involved in the pattern of intra-
and inter-specific variation in  performance in the market task. One approach to
identify candidate mechanisms underlying performance in a cognitive task
is to develop proximate learning models and to evaluated in light of the behavioural data 
(e.g. @dubois_Model_2021). By varying the cognitive tool
kit, one can assess which minimal kit is necessary to solve the task at
hand. This approach has been used to analyse the market task
[@prat_Role_2021; @quinones_Reinforcement_2019]. Learning models showed that basic reinforcement learning does not suffice to solve the task, this is 
particularly so when model assume the more complex natural situation 
in which cleaners
not only face resident-visitor pairs but also visitor-visitor and
resident-resident pairs, as well only a resident or only a visitor. To
be able to give visitors priority over residents, cleaners first need to
be able to assess a client's value separately for the three possible
forms of encounter (alone, paired with a fish with the same strategic
option, paired with a fish with the alternative strategic option)
[@quinones_Reinforcement_2019]. In addition, cleaners need to account for the future
consequences of current decisions. In the model, this could be achieved
in two non-mutually exclusive ways [@quinones_Reinforcement_2019]:
through low temporal discounting of future effects
and/or through perceiving a visitor client leaving as psychological
punishment (i.e. as a negative reinforcer). Given that a negative
reinforcer is part of the ubiquitous learning mechanism termed operant
conditioning (Thorndike xxxx), this explanation can be considered the
simpler one. Furthermore, accounting for the future effects of an action is 
considered an advanced cognitive ability [@suddendorf_Evolution_2007]. 
Here, we fitted our model to the empirical data on fish
densities and cleaner fish performance in the market task with the aim
to determine the likely mechanism used by cleaners to incorporate future
consequences of current decisions.

@@

The model consist of a set individual-based simulations where
individuals face a series of choices between two options. Individuals in
the model represent cleaners, and the options they face simulate the
natural conditions of a cleaning market. Thus, individuals in the model
choose to prioritize different clients. These clients are classified as
resident and visitors. Residents are those clients that stay in the
cleaning queue when they are not given priority; while visitors leave
the queue (with a certain probability) after they are not given
priority. Individuals obtain reward from cleaning a client regardless of
the type. Every time individuals face and make a choice they update the
probability of making that same choice. The update is based on the
difference between the expectation of reward and the actual reward the
individual obtains (prediction error); and it is carried in the
direction that would lead to more reward being obtained, given the new
information. Further details of the model implementation can be found in
the paper [@quinones_Reinforcement_2019]. The model analysis points to
the relevance of two parameters. First, $\gamma$ measures how much
individuals include future rewards in their decision updates. If
$\gamma=0$, individuals only use the immediate reward obtained from a
cleaning interaction. As $\gamma$ increases individuals include more the
reward obtained from the subsequent choices. That amounts to calculating
and using for decision making the future expected rewards in action. Second,
$\eta$ measures how much individuals include in their reward the fleeing
behaviour of visitor clients as a negative component. Both of these
parameters allow individuals to use in their estimates the future
effects of their choices. The model analysis shows that without either
of them, learning individuals cannot develop a preference for the
visitor client. The analysis contrast the effect of these two parameters
against variation in the relative abundance of the two client types. The
analysis shows that under very high client (relative) abundance the presence of
future rewards ($\gamma>0$) no longer favours the preference for the
ephemeral clients, this effect does not occur with negative reward
mediated by client behaviour ($\eta$). Thus, the analysis suggests that
future reward as an explanation for cleaner ability to prefer visitors
is supported by @triki_Biological_2019 data. However, a combination of
future and negative rewards, could still be a better explanation for the
data. In the current analysis, we will use the data from
@triki_Biological_2019 to fit some of the model parameters, particularly
relevant we will fit $\gamma$ and $\eta$ to find out whether each or a
combination of these effects is a better explanation for the pattern
seen in the data. For other parameter values used for the model simulations
and the MCMC see Table \ref{tab:param}

<!-- # ```{r parTable} -->
<!-- # source(here("loadData.R")) -->
<!-- # parFiles<-grep("parametersMCMC",list.files(here("Simulations","MCMCclean_gam_nRew_sca_"), -->
<!-- #                                               full.names = TRUE),value = TRUE) -->
<!-- # params<-fromJSON(parFiles[1]) -->
<!-- # ``` -->

@@

In order to capture with the model the relationship between the
characteristics of the market (environment) and the cleaner's
performance we need to translate the absolute abundances of the data to
relative abundances. This is because in the model, relative abundances
of clients define not only the probability of residents and visitors,
but also how often the cleaning station is empty (e.g. there are no
clients to be cleaned). The more cleaners, the more options available
for the clients and hence higher probability of empty cleaning stations.
How often the cleaning stations are empty in turns influences the value
that cleaners can expect from their choices. The more empty the empty
cleaning stations are, the more it is to choose a client that will not
stay. However, the frequency of empty spots in the cleaning station does
not only depend on cleaner relative abundances but also on the frequency
with which clients visit the station. The client visitation frequency
will likely vary among different clients depending on parasite
abundances and loads. These are variables for which we do not have field
estimates. Thus, we computed a measure of relative cleaner abundance for
each site relative to absolute abundances and multiplied by a scaling
constant that changes the range of the variable. We fit the value of the
scaling constant as part of the statistical inference. As for the client
abundances for residents and visitors we computed a relative measure
with respect to the total client abundance, and weighted that by the
rescaled relative absence of cleaners (1-relative cleaner abundance).
Thus, all three measures of relative abundance sum up to 1, and can be
used in the model as a proxy for the probability of having different
options in the cleaning station.

@@

```{r post, fig.cap="Posterior distributions for parameter values $\\gamma$, $\\eta$ and the scaling constant. We show the kernel density estimates, below the mode (black point) and the 65\\% (light blue) and 95\\% (grey)  highest posterior density interval for the three paramteres. On the left (panels a, c and c) posterior distributions for a model with   all three parameters; while on the right (b and d) a model without negative reward. Panel f shows a measure of fit for both models, namely the distribution of pseudo-$R^2$ obtained from sampling the posterior distribution of parameter values.",out.width='85%'}
knitr::include_graphics(here("post_both_gamma.png"))

@@

The cognitive mechanism that our analysis highlights does not require a direct flow of information between the cleaner and its social environment. The adaptive responses to local conditions in cleaners is not only evidenced by their performance in  experiments, but also by changes in their brain anatomy. Indeed, individual cleaners that performed in the laboratory test according to what is best at the location in which they were caught had larger forebrains harbouring more cells than individuals whose performance mismatched locally optimal decision-rules [@triki_Brain_2020]. This suggests that despite the overall behavioural adjustment, evidenced here and elsewhere 
[@triki_Biological_2019; @triki_Decrease_2018], there are some cleaners better than others at adjusting their behaviour. @triki_Brain_2020 refer to these as socially competent cleaners. Social competence refers to the ability to optimise social behaviour depending on the available social information [@taborsky_Social_2012a;@bshary_Cooperation_2015]. 
However, we have shown here that cleaners are able to adjust their preference 
according to the social environment without using any direct information about the social
environment. Instead cleaners seem to adjust their preference using information from the visitation patterns of their clients. These patters are of course determined by the feedback with the cleaner's social environment (relative abundance). Our models, however, do not include the possibility of cleaners responding to their relative abundance directly. The mechanism we present is a general way to learn from the environment
in both asocial and social situations. It would be interesting to contrast this learning mechanism with one tailored to a social situation, and see whether such mechanism 
fits the data better. More generally, an important challenge ahead is to understand 
which cognitive mechanisms evolved exclusively for social life.

One potential difference between cleaners that adjusted adaptively, like the ones
reported in @triki_Brain_2020, is configurational learning or chunking. The original analysis of the learning model showed that agents needed two mechanism to solve the 
market task; to account for the future, and to assign value to the combination of clients
present in the station [@quinones_Reinforcement_2019]. The latter is referred to as configurational learning or chunking [@sutherland_Configural_1989;@miller_Magical_1956]. 
Theoretical models suggest that the lack of configurational learning is related to a low 
frequency with which stimuli are encountered together [@kolodny_Evolution_2014;@prat_Role_2021]. Thus, cleaner relative abundance could be related to this mechanisms as well. Given that the lack of either of these two mechanisms yields 
neutral preferences [@quinones_Reinforcement_2019], we can't, based on the current analysis, distinguish between the two possibilities. One potential way to distinguish between the two would be to use an experimental set up designed to test configuration learning on cleaners
with high and low performance in the market task [@woodbury_Learning_1943;@sutherland_Configural_1989].

Combining mechanistic modelling with empirical data provides a powerful tool to identify the cognitive processes underlying learning in animals. The combination overcomes the limitations of the general philosophy in animal cognition to apply the logic of Lloyd Morgen’s canon (Occam’s razor). Excluding basic reinforcement learning explanations (operant and/or classical conditioning) as a potential explanation in experiments often warrants animals solving the task on the first possible occasion. For example, any theory of mind task needs to be solved in the first trial in order to exclude fast conditioning [@heyes_Theory_1998]. Similarly, subjects need to solve a social learning task on the first trial to accept imitation as a mechanism over stimulus/local enhancement. Such strict conditions are virtually never met. For example, potato washing by Japanese macaques, an iconic example of social learning, took several years to spread within the group [@kawamura_Process_1959], meaning that any learner had been repeatedly exposed to demonstrations before acquisition. Importantly, @galef_Question_1992 refuted imitation as mechanism not simply because of the repeated exposure but because a (rather qualitative) analysis of the spread of potato washing across individuals did not follow the prediction based on imitation learning (see also @hirata_SweetPotato_2001). In our case, the number of trials it took cleaners to learn the solution to the market task would never allow to exclude an important role of negative reinforcement based on the data alone. However, fitting model predictions to our data set revealed that a more complex mechanism (estimation of future reward) fits the data better.

>>>>

One example of strategic adjustment in a biological market is the marine
cleaning mutualism involving the cleaner fish *Labroides dimidiatus* and
'client' fish. Clients offer themselves as food patches for cleaners to
remove ectoparasites, which gives the cleaners calories and the clients
improved health [@waldie_LongTerm_2011;
@ros_Does_2011,@triki_Effects_2016]. As cleaners have about 2000
interactions per day [@grutter_Relationship_1995], they regularly face
the situation that two clients seek cleaning simultaneously. In such
conditions, it is important to distinguish between 'resident' and
'visitor' client species [@bshary_Cleaner_2001a]. The residents have
small home ranges and hence access to only the local cleaner, while the
visitors have large home ranges and hence access to two or more
cleaners. Thus, visitors have the option to switch to another cleaner if
being made to wait, while residents must wait for inspection. Indeed,
visitors have been observed to use their partner choice options in that
way [@bshary_Choosy_2002], which may explain why cleaners give
visitors service priority in a field study in the Red Sea
[@bshary_Cleaner_2001a]. More generally, cleaners apparently prefer to
interact with visitors [@triki_Zeni_inpress]. Such a preference may be
linked to a client's value as a food patch; visitors are on average
larger than residents [ @bshary_Cleaner_2001a], and size is positively
correlated with parasite load(Grutter xxxx). However, early laboratory
experiments showed that leaving causes service priority independent of
client value [@bshary_Asymmetric_2002]. The experiments consisted of a
simultaneous two-choice task, where cleaners had to decide which of two
Plexiglas plates, which offered equal amounts of food, to approach first
and eat mashed prawn of it. One plate was made to behave like a
resident, i.e. it would remain until the cleaner had eaten off it. The
other plate was made to behave like a visitor, i.e. it would be removed
if not inspected first. Cleaners learned to prefer the visitor plate and
hence obtained the double amount of food [@bshary_Asymmetric_2002].
Adult cleaner fish outperform various primates as well as rats and
pigeons in this original version of the biological market task
[@salwiczek_Adult_2012; @zentall_Early_2017]; only African grey
parrots solve this task as well [@pepperberg_Can_2014].

Recent research has refined our view on partner choice and priority of
access in the *L. dimidiatus* cleaning mutualism, and as a consequence
performance in the biological market task. First, details of the task
presentation may matter; i.e. what relevant information is encoded in
the design of the two plates (colour versus size;
@wismer_Cuebased_2019), or whether the information is in the colour of
the food [@pretot_Comparative_2021; @pretot_Comparing_2016], and
whether the food is visible or hidden/released only when the subjects
made choices on a touch screen [@pretot_Factors_2016]. Second, it
appears that cleaner and client densities in nature affect how cleaners
perform in the original market task: when densities are low, cleaners
are more likely to fail to complete the task [@triki_Biological_2019;
@triki_Decrease_2018; @wismer_Variation_2014]. The apparent explanation
for this failure is that visitor clients are less likely to exert their
choice options (and hence wait for inspection if made to wait) when
cleaner fish densities are low [@triki_Brain_2020]. This change in
behaviour may be due to the fact that when cleaner densities are low,
the cost of switching in terms of distance to swim and time invested
increases. If visitors are not choosy, cleaners should not give them
priority anymore. Interestingly, while cleaners from high-density areas
have larger forebrains harbouring more cells than cleaners from
low-density areas [@triki_Brain_2020], on a local scale those
individuals that perform in the market task in a way that corresponds to
the locally optimal strategy (solving/failing the task when living in
high/low density) have relatively larger forebrains [@triki_Brain_2020].
Taken together, empirical results clearly show major intra- and
inter-specific variation in performance in the market task, warranting
investigation of the underlying cognitive machinery, from perception to
decision-making [@shettleworth_Cognition_2009].

One approach to identify candidate mechanisms underlying performance in
a cognitive task is to develop proximate learning models and to evaluate
their predictions in light of the behavioural data (e.g.
@dubois_Model_2021). By varying the cognitive tool kit, one can assess
which minimal kit is necessary to solve the task at hand. This approach
has been used to analyse the market task [@prat_Role_2021;
@quinones_Reinforcement_2019]. Learning models showed that basic
reinforcement learning does not suffice to solve the task, this is
particularly so when models assume the more complex natural situation in
which cleaners not only face resident-visitor pairs but also
visitor-visitor and resident-resident pairs, as well only a resident or
only a visitor. To be able to give visitors priority over residents,
cleaners first need to be able to assess a client's value separately for
the three possible forms of encounter (alone, paired with a fish with
the same strategic option, paired with a fish with the alternative
strategic option) [@quinones_Reinforcement_2019]. In addition, cleaners
need to account for the future consequences of current decisions. In the
model, this could be achieved in two non-mutually exclusive ways
[@quinones_Reinforcement_2019]: through low temporal discounting of
future effects and/or through perceiving a visitor client leaving as
psychological punishment (i.e. as a negative reinforcer). Given that a
negative reinforcer is part of the ubiquitous learning mechanism termed
operant conditioning (Thorndike 1917), this explanation can be
considered the simpler one. Furthermore, accounting for the future
effects of an action is considered an advanced cognitive ability
[@suddendorf_Evolution_2007]. Here, we fitted our model to the empirical
data on fish densities and cleaner fish performance in the market task
with the aim to determine the likely mechanism used by cleaners to
incorporate future consequences of current decisions.

@@

The model consist of a set individual-based simulations where
individuals face a series of choices between two options. Individuals in
the model represent cleaners, and the options they face simulate the
natural conditions of a cleaning market. Thus, individuals in the model
choose to prioritize different clients. These clients are classified as
resident and visitors. Residents are those clients that stay in the
cleaning queue when they are not given priority; while visitors leave
the queue (with a certain probability) after they are not given
priority. Individuals obtain a fixed reward from cleaning a client
regardless of the type. Every time individuals face and make a choice
they update the probability of making that same choice. The update is
based on the difference between the expectation of reward and the actual
reward the individual obtains (prediction error)
[@sutton_Reinforcement_2018; \@rescola_Theory_1972]; and it is carried
in the direction that would lead to more reward being obtained, given
the new information. Further details of the model implementation can be
found in the paper [@quinones_Reinforcement_2019]. The model analysis
points to the relevance of two parameters. First, $\gamma$ measures how
much individuals include future rewards in their decision updates. If
$\gamma=0$, individuals only use the immediate reward obtained from a
cleaning interaction. As $\gamma$ increases individuals include more the
reward obtained from the subsequent choices. That amounts to calculating
and using for decision making the future expected rewards in action.
Second, $\eta$ measures how much individuals include in their reward the
fleeing behaviour of visitor clients as a negative component. Both of
these parameters allow individuals to use in their estimates the future
effects of their choices. The model analysis by
@quinones_Reinforcement_2019 shows that without either of them, learning
individuals cannot develop a preference for the visitor client. The
analysis contrast the effect of these two parameters against variation
in the relative abundance of the two client types. The analysis shows
that under very high client (relative) abundance the presence of future
rewards ($\gamma>0$) no longer favours the preference for the ephemeral
clients, this effect does not occur with negative reward mediated by
client behaviour ($\eta$). Thus, the analysis suggests that future
reward as an explanation for cleaner ability to prefer visitors is
supported by @triki_Biological_2019 data. However, a combination of
future and negative rewards, could still be a better explanation for the
data. In the current analysis, we will use the data from
@triki_Biological_2019 to fit some of the model parameters, particularly
relevant we will fit $\gamma$ and $\eta$ to find out whether each or a
combination of these effects is a better explanation for the pattern
seen in the data. For other parameter values used for the model
simulations and the MCMC see Table \ref{tab:param}

@@

In order to capture with the model the relationship between the
characteristics of the market (environment) and the cleaner's
performance we need to translate the absolute abundances of the data to
relative abundances. This is because in the model, relative abundances
of clients define not only the probability of residents and visitors,
but also how often the cleaning station is empty (e.g. there are no
clients to be cleaned). The more cleaners there are, the more options
are available for the clients and hence the higher is the probability of
empty cleaning stations. How often the cleaning stations are empty in
turns influences the value that cleaners can expect from their choices.
The emptier the cleaning stations are, the more benefitial it is to
prioritize a client that will not stay. However, the frequency of empty
spots in the cleaning station does not only depend on cleaner relative
abundances but also on the frequency with which clients visit the
station. The client visitation frequency will likely vary among
different clients depending on parasite abundances and loads. These are
variables for which we do not have field estimates. Thus, we computed a
measure of relative cleaner abundance for each site relative to absolute
abundances and multiplied by a scaling constant that changes the range
of the variable. We fit the value of the scaling constant as part of the
statistical inference. As for the client abundances for residents and
visitors we computed a relative measure with respect to the total client
abundance, and weighted that by the rescaled relative absence of
cleaners (1-relative cleaner abundance). Thus, all three measures of
relative abundance sum up to 1, and can be used in the model as a proxy
for the probability of having different options in the cleaning station.

@@

```{r post, fig.cap="Posterior distributions for parameter values $\\gamma$, $\\eta$ and the scaling constant. We show the kernel density estimates, below the mode (black point) and the 65\\% (light blue) and 95\\% (grey)  highest posterior density interval for the three paramteres. On the left (panels a, c and c) posterior distributions for a model with   all three parameters; while on the right (b and d) a model without negative reward. Panel f shows a measure of fit for both models, namely the distribution of pseudo-$R^2$ obtained from sampling the posterior distribution of parameter values.",out.width='95%'}
knitr::include_graphics(here("post_both_gamma.png"))

@@

The cognitive mechanism that our analysis highlights does not require a
direct flow of information between the cleaner and its social
environment. The adaptive responses to local conditions in cleaners is
not only evidenced by their performance in experiments, but also by
changes in their brain anatomy. Indeed, individual cleaners that
performed in the laboratory test according to what is best at the
location in which they were caught had larger forebrains harbouring more
cells than individuals whose performance mismatched locally optimal
decision-rules [@triki_Brain_2020]. This suggests that despite the
overall behavioural adjustment, evidenced here and elsewhere
[@triki_Biological_2019; @triki_Decrease_2018], there are some
cleaners better than others at adjusting their behaviour.
@triki_Brain_2020 refer to these as socially competent cleaners. Social
competence refers to the ability to optimise social behaviour depending
on the available social information [@taborsky_Social_2012a;
@bshary_Cooperation_2015]. However, we have shown here that cleaners
are able to adjust their preference according to the social environment
without using any direct information about the social environment.
Instead cleaners seem to adjust their preference using information from
the visitation patterns of their clients. These patters are of course
determined by the feedback with the cleaner's social environment
(relative abundance). Our models, however, do not include the
possibility of cleaners responding to their relative abundance directly.
The mechanism we present is a general way to learn from the environment
in both asocial and social situations. It would be interesting to
contrast this learning mechanism with one tailored to a social
situation, and see whether such mechanism fits the data better. More
generally, an important challenge ahead is to understand which cognitive
mechanisms evolved exclusively for social life.

One potential difference between cleaners that adjusted adaptively, like
the ones reported in @triki_Brain_2020, is configurational learning or
chunking. The original analysis of the learning model showed that agents
needed two mechanism to solve the market task; to account for the
future, and to assign value to the combination of clients present in the
station [@quinones_Reinforcement_2019]. The latter is referred to as
configurational learning or chunking [@sutherland_Configural_1989;
@miller_Magical_1956]. Theoretical models suggest that the lack of
configurational learning is related to a low frequency with which
stimuli are encountered together [@kolodny_Evolution_2014;
@prat_Role_2021]. Thus, cleaner relative abundance could be related to
this mechanisms as well. Given that the lack of either of these two
mechanisms yields neutral preferences [@quinones_Reinforcement_2019],
we can't, based on the current analysis, distinguish between the two
possibilities. One potential way to distinguish between the two would be
to use an experimental set up designed to test configuration learning on
cleaners with high and low performance in the market task
[@woodbury_Learning_1943; @sutherland_Configural_1989].

Combining mechanistic modelling with empirical data provides a powerful
tool to identify the cognitive processes underlying learning in animals.
The combination overcomes the limitations of the general philosophy in
animal cognition to apply the logic of Lloyd Morgen's canon (Occam's
razor). Excluding basic reinforcement learning explanations (operant
and/or classical conditioning) as a potential explanation in experiments
often warrants animals solving the task on the first possible occasion.
For example, any theory of mind task needs to be solved in the first
trial in order to exclude fast conditioning [@heyes_Theory_1998].
Similarly, subjects need to solve a social learning task on the first
trial to accept imitation as a mechanism over stimulus/local
enhancement. Such strict conditions are virtually never met. For
example, potato washing by Japanese macaques, an iconic example of
social learning, took several years to spread within the group
[@kawamura_Process_1959], meaning that any learner had been repeatedly
exposed to demonstrations before acquisition. Importantly,
@galef_Question_1992 refuted imitation as mechanism not simply because
of the repeated exposure but because a (rather qualitative) analysis of
the spread of potato washing across individuals did not follow the
prediction based on imitation learning (see also
@hirata_SweetPotato_2001). In our case, the number of trials it took
cleaners to learn the solution to the market task would never allow to
exclude an important role of negative reinforcement based on the data
alone. However, fitting model predictions to our data set revealed that
a more complex mechanism (estimation of future reward) fits the data
better.
